%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Education}
% 
%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Professional Data Engineer} % Degree
{Google Cloud Certification} % Institution
{} % Location
{Jun. 2020 - Jun. 2022} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
	\item {Attest-id: F2TUNC}
	\item {Link to attest: \href{https://www.credential.net/4c80a182-e4d8-4c0b-8e55-1180970b287c}{https://www.credential.net/4c80a182-e4d8-4c0b-8e55-1180970b287c}}
\end{cvitems}
}


\cventry
{MSc. in Computer Science} % Degree
{UCPH (University of Copenhagen)} % Institution
{} % Location
{Nov. 2014} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item {Elective Project: Hybridization of mesh-free and mesh based simulation methods\\
		\phantom{x}\scriptsize{developed using MATLAB, grade: 10}}
\item {Studied a semester abroad (aug. - dec. 2013) at the \textit{University of British Columbia}, Vancouver - Canada}
\item {Master's Thesis: The Use of Moving Meshes for Segmentation and Registration of 2D Medical Imaging\\
		\phantom{x}\scriptsize{developed using C++, grade: 12}}
\end{cvitems}
}

\cventry
{Exchange Student} % Degree
{UBC (University of British Columbia)} % Institution
{} % Location
{Aug. 2013 - Dec. 2013} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item {I studied a semester abroad, at UBC in Vancouver - Canada}
\end{cvitems}
}

\cventry
{BSc. in Computer Science} % Degree
{UCPH (University of Copenhagen)} % Institution
{} % Location
{Jun. 2012} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item {BSc. Project: Using Compounds of Convex Shapes in Interactive Rigid Body Simulation\\
		\phantom{x}\scriptsize{developed using C++, grade: 12}}
\end{cvitems}
}

\cventry
{Mathematical Student} % Degree
{Frederiksberg Gymnasium} % Institution
{} % Location
{Jul. 2007} % Date(s)
{ % Description(s) bullet points
}

%------------------------------------------------

\end{cventries}
