%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Professional Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Cloud Data Scientist/Engineer} % Job title
{GroupM} % Organization
{} % Location
{Apr. 2020 - Jul. 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented on-site behavior based customer targeting strategies using Machine Learning.}
\item {Consulting for clients of the bureau on Data Science \& Data Engineering tasks.}
\item {Created and improved products for novel marketing campaigns \& strategies based on first party data.}
\item {Worked cross-department to provide the bureaus with customized data-based marketing solutions.}
\item {Achieved certification on Google Cloud. Most projects carried out in Googles Cloud environment.}
\item {Most frequent Google Cloud services used: BigQuery, BigQueryML, AutoML, Cloud Functions, Pub/Sub, Firestore}
\item {Used Microsoft Azure for certain client consultancy jobs.}
\item {Most frequent Microsoft Azure services used: DataBricks, DataLake Storage, CosmosDB}
\end{cvitems}
}


\cventry
{Machine Learning Engineer} % Job title
{Paperflow} % Organization
{} % Location
{Mar. 2018 - Apr. 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developing a Machine Learning solution to classify invoices by creditor and match these to a customer provided catalog}
\item {Worked on a Machine Learning model for digitally flattening creased documents, based on methodologies from published academic research}
\item {Developing scanner engine to perform automatic bookkeeping of invoices, including document recognition and classification}
\item {Performing prototyping experiments using ML techniques such as: convolutional nerual networks, transfer learning \& natural language processing}
\item {All programming work done in Python}
\item {Using Tensorflow, Keras, Fastai, Jupyter Notebooks, Numpy, Scipy \& Pandas for performing Data Science tasks}
\item {Collecting and structuring data sets from multiple data sources as well as understanding and cleaning data}
\item {Working with Google Cloud for manipulating stored data, handling virtual machines and training \& deploying ML models}
\end{cvitems}
}

\cventry
{Full Stack Engineer} % Job title
{Coinify} % Organization
{} % Location
{Dec. 2016 - Mar. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developer on a platform for facilitating bitcoin merchanting and trading}
\item {Full-stack Node.js, TypeScript and PHP development work}
\item {Working with AWS for manipulating stored data and deploying code to production}
\end{cvitems}
}

\cventry
{Software Developer} % Job title
{Gamblify} % Organization
{} % Location
{Nov. 2014 - Jan. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Full-stack developer of online casino games}
\item {Created front end client using Javascript \& Dart}
\item {Made great extensions to existing server and game logic in Java}
\end{cvitems}
}

\cventry
{Teaching Assistant} % Job title
{University of Copenhagen} % Organization
{} % Location
{Sep. 2011 - Nov. 2011 \& Feb. 2013 - Jun. 2013} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Employed for the courses: \textit{Datanet}, \textit{Foundations of Computer Graphics} \& \textit{Human Computer Interaction}}
\item {Co-responsible for course planing \& development of programming assignments in Python and C++}
\item {Responsible for execution of exercise classes, correction of assignments and general student guidance.}
\end{cvitems}
}
\cventry
{Student DevOps} % Job title
{Magasin Du Nord} % Organization
{} % Location
{Jan. 2012 - Sep. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Responsible for IT operations and support for all 6 Magasin stores in Denmark on weekday evenings and weekends.}
\item {Developed further extentions for an existing piece of software for hand held scanners in C\#}
\end{cvitems}
}

% %------------------------------------------------

\end{cventries}
