%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Talks}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {The AI Revolution: Trends you have to know} % Title
    {ComputerWorld Summit} % Event
    {Dansk Industri} % Location
    {May 2024} % Dat(s)
    {
      A talk on the current trends and hottest topics in AI.
    }

    \cventry
    {SkoleGPT} % Title
    {Driving AI (IDA)} % Event
    {IDA Conference} % Location
    {May 2024} % Date(s)
    {
      A talk together with Martin Exner of Københavns Professionshøjskole on the process and future perspective of the SkoleGPT project I helped create.
    }

    \cventry
    {(AI) Masterclass} % Title
    {Nutanix} % Event
    {ComputerWorlds studio} % Location
    {May 2024} % Date(s)
    {
      I cohosted an online Masterclass on AI together with Thomas Jensen from Nutanix.
    }

    \cventry
    {AI in the Travel Industry} % Title
    {Dansk Erhverv/Danmarks Rejsebureau Forening (DRF)} % Event
    {Aller Medier} % Location
    {Apr. 2024} % Date(s)
    {
      A talk on AI and its influence and use in the travel industry, originally planned to be hosted at Børsen but moved due to fire.
    }

    \cventry
    {AI in the Beauty Industry} % Title
    {Beauty 2024} % Event
    {Bella Centret} % Location
    {Mar. 2024} % Date(s)
    {
      A talk on how AI is used within the beauty industry.
    }

    \cventry
    {Generative AI \& the Future of Work} % Title
    {VL Group 53} % Event
    {Company Onsite} % Location
    {Jan. 2024} % Date(s)
    {
      A talk on the last 6 months development within AI and how these trends can affect the future of work.
    }


    \cventry
    {Safe Applications of AI on your own Data} % Title
    {COMPUTERWORLD - AI Business Excellence Day} % Event
    {Virtual} % Location
    {Dec. 2023} % Date(s)
    {
      I gave a talk on how businesses can apply AI LLMS on their own data without compromising security. I also showcases uses for this technology.
    }

    \cventry
    {Wilder Generative AI} % Role
    {Driving IT} % Event
    {IDA - Copenhagen} % Location
    {Nov. 2023} % Date(s)
    {
      I gave a talk on generative AI and what progress we will see in the near and distant future.
    }

    \cventry
    {3 Impressive Cases of Applied AI} % Role
    {ComputerWorld Cloud Festival} % Event
    {Copenhagen} % Location
    {Sep. 2023} % Date(s)
    {
      I gave a talk together with Søren Christian Søndergaard Poulsen showcasing some of the most impressive usecases of AI both in Denmark and internationally.
    }

    \cventry
    {SkoleGPT Presentation} % Role
    {Internal Presentation} % Event
    {UFST (Skat) - Copenhagen} % Location
    {Sep. 2023} % Date(s)
    {
      I gave a talk at UFST on my work in developing SkoleGPT as well as the experiences I've gained in working with cutting edge Large Language Models.
    }

    \cventry
    {Deep Generative Models} % Role
    {Driving IT} % Event
    {IDA - Copenhagen} % Location
    {Nov. 2022} % Date(s)
    {
      I gave a talk on Generative AI, its history and progress (right before ChatGPT came out).
    }

    \cventry
    {8 years of Deep Generative Machine Learning} % Role
    {PyData Copenhagen} % Event
    {Alm Brand - Copenhagen} % Location
    {Sep. 2022} % Date(s)
    {
      I gave a talk on the exciting and rapidly progressing history of Deep Generative ML and also showcased some of my own creative work.
    }


%---------------------------------------------------------
\end{cventries}