%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Workshops \& Courses}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Agentic AI} % Title
{PNO} % Client
{Half day workshop} % Duration/Type
{Mar 2025} % Date(s)
{
  Follow-up workshop on agentic AI held with Philip Petersen from Prehype. Included an introductory talk on the underlying technology and mechanics of agentic AI, followed by hands-on sessions where participants explored practical applications. Served as technical expert and facilitator, assisting participants with implementation questions throughout the workshop.
}

\cventry
{AI \& Prompting for Librarians} % Title
{Herning Bibliotekerne} % Client
{2 day workshop} % Duration/Type
{Sep 2024} % Date(s)
{
  Included an internal course and an open workshop for libraries across Jutland, covering prompting, image and video generation, advanced AI tools, songwriting with AI, chatbot building, and responsible use of the technology.
}

\cventry
{AI in the Nordic Setting} % Title
{Nordisk Ministerråd} % Client
{2 hour mini-workshop} % Duration/Type
{Aug 2024} % Date(s)
{
   Mini workshop on modern AI technologies and their applications in communication and policy across the Nordic region. Covered how language models like ChatGPT work, their use in public administration, and the representation of Nordic languages in large language models.
}

\cventry
{AI \& Prompt Engineering} % Title
{Lemvigh-Müller} % Client
{90 minute segment with workshop} % Duration/Type
{Jun 2024} % Date(s)
{
  A talk and workshop for top management covering the transformative nature of modern AI, fundamentals of prompt engineering, hands-on activities to invoke curiosity, discussions on AI's impact on work, and ethical considerations.
}

\cventry
{AI \& ChatGPT Workshop} % Title
{Pharma4Ever} % Client
{Full Day Workshop} % Duration/Type
{May 2024} % Date(s)
{
  Focused on generative AI in the pharmaceutical industry, including fundamentals, applications of ChatGPT, hands-on assignments with advanced AI tools, discussions on potential and ethical concerns.
}

\cventry
{Generative AI for Journalism} % Title
{Danmarks Medie og Journalisthøjskole (DMJX)} % Client
{Full day Course} % Duration/Type
{March 2024, May 2024 \& May 2025} % Date(s)
{
  Courses on using generative AI for journalism, including text and image generation with ChatGPT and DALL-E 3, hands-on assignments, and discussions on ethical considerations.
}

\cventry
{Generative AI @ Danske Spil} % Title
{Danske Spil} % Client
{90 minute intensive workshop} % Duration/Type
{2024} % Date(s)
{
  Part of a kickoff conference, includes intro to prompt engineering, case study, group assignments on applying Danske Spil products to new user segments, and result discussions.
}

\cventry
{Get Started on Generative Images/Video/Audio} % Title
{PROSA} % Client
{3 hour after work workshop} % Duration/Type
{May 2024 \& September 2023} % Date(s)
{
  Focus on visual/audial generative AI tools, open workshop format, emphasis on collaboration and result sharing.
}

\cventry
{ChatGPT for IT-Professionals} % Title
{Dansk IT} % Client
{2 day and 1 day course} % Duration/Type
{November 2023, March 2024} % Date(s)
{
  Workshop on ChatGPT application for IT professionals, including hands-on assignments, discussions on AI landscape and ethical considerations.
}

\cventry
{Generative AI Workshop} % Title
{Transmission Learning} % Client
{Full day workshop} % Duration/Type
{2023} % Date(s)
{
  Conducted six times, focus on generative AI for text and image generation, hands-on assignments, discussions on practical applications and ethical considerations.
}


%---------------------------------------------------------
\end{cventries}